Placeholder

### 2021-02-06 Paper_Histograms.Rmd
Plotted positive diagnosis/control for GLAD/EDGI prepan

@@

@@

@@

#### Plot Style 1

@@

####Plot Style 2

>>>>

COPINGpalette11 <- c("#78D9C5",
                    "#F5BE5E",
                    "#EEB6E9",
                    "#DBDB73", 
                    "#FFED98",
                    "#BFD2EB", 
                    "#808080",
                    "#cccccc",
                    "3B47DA",
                    "#b7dee8",
                    "#F567F3")

@@

#####Plot positive diagnosis prepan

```{r Plot GLAD/EDGI prepan positive diagnosis}

GLAD.prepan_positive_diagnosis_GLADEDGI %>% 
  ggplot(aes(x = reorder(Diagnosis, -positive_n), y = positive_n)) +
  geom_bar(stat = "identity", fill = COPINGpalette11) + 
  scale_fill_manual(values = COPINGpalette11) +
  theme_minimal() +
  theme(plot.title = element_text(hjust = 0.5),
        plot.subtitle = element_text(hjust = 0.5)) +
  labs(title = "Mental health diagnoses of the GLAD/EDGI prepan cohort",
       subtitle = paste("N =", dim(GLAD.retro)[1]),
         x = "",
       y = "") +
  scale_x_discrete(guide = guide_axis(n.dodge = 2)) +
  theme(legend.position = "top") + 
  theme(legend.title = element_blank())

###Retro
####Get positive diagnoses

@@

```
####Merge and clean the data

@@

#####Plot Style 1

@@

#####Plot Style 2
